Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-08-01 article_springer/article_springer.Rmd
Change Remark after Proof according file with Comments to Referees

: If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant. [@MeerschaertStoev08] proofed a limit theorem for the maxima of iid random variables separated by infinite mean waiting times. They showed that the duration time of the limit process is Mittag-Leffler distributed. [@Basrak2014] described the asymptotic distribution under similar assumptions of all upper orders statistics using point processes.

>>>>

: If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant. [@MeerschaertStoev08] proved a limit theorem for the maxima of iid random variables separated by infinite mean waiting times. They have also shown that the hitting time of the limit process is Mittag-Leffler distributed. [@Basrak2014] described the asymptotic distribution, under similar assumptions, of all upper orders statistics using point processes.
